\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in, top=0.4in, right=0.4in, bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Jayaditya Dev} % Your name

% Contact Information
\address{+91 92345 09450 \\ Bengaluru, Karnataka, IN}
\address{\href{mailto:jayadityadev26@outlook.com}{jayadityadev26@outlook.com} \\ 
\href{https://linkedin.com/in/jayadityadev26}{linkedin.com/in/jayadityadev26} \\ 
\href{https://github.com/jayadityadev}{github.com/jayadityadev}}

\begin{document}

\vspace{0.5em}

%----------------------------------------------------------------------------------------
% OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}
    Aspiring cybersecurity professional and programmer seeking to contribute to impactful projects through skills in penetration testing, vulnerability assessment, and automation, while continuing to learn and grow within a forward-thinking organization.
\end{rSection}

\vspace{0.5em}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Programming Languages & Python, C, C++, Java, Rust, DSA \\
        Cybersecurity Skills & Penetration Testing, Vulnerability Assessment, Network Security \\
                             & Incident Response, Secure Programming, Cloud Security \\
        Tools               & Git, VMs, Docker, Wireshark, Metasploit, BurpSuite, AWS (EC2, S3, Lambda) \\
        Operating Systems   & Windows, Linux (all major distributions) \\
        Soft Skills         & Leadership, Communication, Problem Solving, Teamwork, Time Management \\
    \end{tabular}
\end{rSection}

\vspace{0.5em}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS}

    \textbf{Penetration Testing, Incident Response, and Forensics} \hfill IBM (Coursera) \\
    \href{https://coursera.org/verify/QWR9Z0N2R813}{coursera.org/verify/QWR9Z0N2R813}

    \vspace{0.1em}
    \textbf{Foundations of Cybersecurity} \hfill Google (Coursera) \\
    \href{https://coursera.org/verify/KN4D2GBJPXCL}{coursera.org/verify/KN4D2GBJPXCL}

    \vspace{0.1em}
    \textbf{Java Essentials, Java OOPs Concepts, and Programming Fundamentals: \\Command Line Interface \& Operating Systems} \hfill Infosys Springboard \\
    \href{https://drive.google.com/drive/folders/1ku7JYTjOOhCaDRoSzWsCSC2EQIBROlZ5?usp=sharing}{drive.google.com}
    
\end{rSection}

\vspace{0.5em}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

    \textbf{Rust-based Search Engine with MongoDB} \hfill [Dec 2024] \\
    \textit{Personal Project} \vspace{0.1em}
    \begin{itemize}
        \itemsep -3pt
        \item Engineered a high-performance search engine using Rust and MongoDB, achieving a 40\% improvement in query response times in initial benchmarking.
        \item Developed and deployed a RESTful API using Actix-web, reducing API latency by 25\% and ensuring seamless frontend-backend communication.
        \item Implemented CORS security policies, mitigating cross-origin security risks and strengthening backend security compliance.
    \end{itemize}

    \vspace{0.2em}
    \textbf{Predictive Analytics for Disease Spread} \hfill [Nov 2024] \\
    \textit{College Project} \vspace{0.1em}
    \begin{itemize}
        \itemsep -3pt
        \item Designed and trained a predictive model for COVID-19 daily death forecasting using a dataset of 1.05 million individuals, leveraging Facebook Prophet for 90\%+ accuracy.
        \item Optimized historical data preprocessing pipelines, reducing data transformation time by 35\% and improving model training efficiency.
        \item Visualized forecast trends with Matplotlib, enabling data-driven policy formulation for pandemic response teams.
    \end{itemize}

\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

    \textbf{Freelance Security Enthusiast} \hfill [2024 - Present] \\
    \textit{Freelancer} \vspace{0.1em} \hfill \textit{Remote}
    \begin{itemize}
        \itemsep -3pt
        \item Developed automation scripts using Linux shell scripting, reducing administrative workload by 30\% and streamlining security audits.
        \item Conducted penetration testing simulations with Burp Suite, Metasploit, and Wireshark, uncovering 10+ security vulnerabilities per engagement and proposing mitigation strategies.
        \item Performed vulnerability assessments on mock systems, strengthening security postures and ensuring best-practice compliance.
    \end{itemize}

\end{rSection}

\vspace{0.5em}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

    \textbf{Bachelor of Engineering}, KS Institute of Technology, Bengaluru \hfill Expected 2027 \\
    CGPA (Upto 2nd semester): 9.25
    \vspace{0.2em}

    \textbf{Class 12th, CBSE Board}, SR DAV Public School, Ranchi \hfill 2023 \\
    Percentage: 84.6\%
    \vspace{0.2em}

    \textbf{Class 10th, CBSE Board}, SR DAV Public School, Ranchi \hfill 2021 \\
    Percentage: 96\%
    
\end{rSection}

\vspace{0.5em}

%----------------------------------------------------------------------------------------
% ADDITIONAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ADDITIONAL INFORMATION}

    \textbf{Achievements}
    \begin{itemize}
        \item Ranked in the top 5\% globally on TryHackMe for CTF challenges. \\ 
        \href{https://tryhackme.com/r/p/jayadityadev}{tryhackme.com/r/p/jayadityadev}
    \end{itemize}

    \vspace{0.2em}
    
    \textbf{Extra-curricular Activities}
    \begin{itemize}
        \item Member of the KS Institute of Technology College Table Tennis Team. \\
              Represented the college in inter-college table tennis tournaments, demonstrating teamwork and sportsmanship.
        \item Interests: Playing CTFs, Guitar, Ukulele, Music, Fitness, Reading, Writing.
    \end{itemize}

    \vspace{0.2em}
    
    \textbf{Languages}
    \begin{itemize}
        \item English (Fluent)
        \item Hindi (Fluent)
    \end{itemize}

\end{rSection}

\end{document}
